\documentclass[12pt, letterpaper]{article}
\usepackage{fancyhdr}
\usepackage[margin=1.87cm]{geometry}%rounded up from 1.87, just to be safe...
%\usepackage{parskip}
\usepackage{times} %make sure that the times new roman is used

\usepackage{xspace}
\newcommand{\etal}{\hbox{\emph{et al.}}\xspace}
\newcommand{\eg}{\hbox{\emph{e.g.,}}\xspace}
\newcommand{\ie}{\hbox{\emph{i.e.}}\xspace}

\usepackage{url}

\makeatletter
\renewcommand{\section}{\@startsection
{section}%		     % the name
{1}%			     % the level
{0mm}%			     % the indent
%{-\baselineskip}%	      % the before skip
{.75mm}
{.03\baselineskip}%	     % the after skip
{\normalfont\large\bf} % the style
}

\begin{document}

\fancyhead{}
%\fancyhf{}
\pagestyle{fancy}
\rhead{Test Prioritization and Localization at Ericsson -- 309207-- \textbf{Peter C Rigby}} %This puts your name at the top right, outside the margin
\renewcommand{\headrulewidth}{0pt}

\begin{center}
\begin{LARGE}
\noindent
\center{{\bf Budget Justification}}
\end{LARGE}
\end{center}

\pagenumbering{gobble}

We plan to support one PhD student and one masters student with this grant.
The students will be under the direct supervision of Dr. Rigby. 
%
Both student will be supported for 6 months by the proposed grant, with
\$11,500 and \$13,000 going to the masters and PhD student, respectively. If
the proposed grant is successful, we will discuss a MITACS grant with Ericsson
to continue this work.

As discussed in the proposal, the recruited masters student will work
directly onsite during this grant to mine, link, and model Ericsson data.

One of Rigby's PhD students, Rahman, will investigate test prioritization in
the context of release engineering. As we discussed in the proposal, releases
can be slowed down by repeated test runs and failures. Rahman's PhD topic is in
release engineering, and a chapter on test prioritization would make an
interesting novel addition in his thesis. It would also expose him to
interesting new datasets and methodologies used by Ericsson. There is no
expectation of intellectual property issues as the findings involve the
Ericsson development environment instead of Ericsson products.

We will need a small budget to travel to Ericsson Ottawa for meetings (\$500).

\end{document}
