\section*{Research Management and Training of HQP}

Students will spend $2/3^{rds}$ of their time conducting research onsite at Ericsson. The remaining $1/3^{rd}$ will be spend at Concordia. While at Ericsson student will mine software test data, apply research methods to this data, and present the results through tools to Ericsson engineers. At Concordia they will generalize their findings to other projects, take required courses, and investigate the feasibility of techniques learned in class to advance the state of the testing art. Students may spend additional semester at Concordia finish their research theses.

At any time, there will be two to three students at Ericsson and one to two at Concordia. Students will be managed day-to-day at Ericsson by McKenna and Griffiths. Rigby will be at Ericsson one day per week to help students with research, mining, and analytics approaches. At Concordia, students will work in our research labs.
%
Students will learn to formulate research questions, collect and clean data, create scripts to operationalize measures, store and link measures and concepts in databases, and use data mining techniques and statistical analyses to answer our research questions. They will also operationalize their research work in the TestGuru tool.

In the table below, we describe the number and type of students that will be working on each proposed milestone. The table is followed by a description of how each research topic is interrelated allowing for synergistic work within our research groups.

%https://docs.google.com/spreadsheets/d/1o7cTGi406Mc8Qx4KWPOByfPNKhB4lydCUQb_G4ngzrE/edit#gid=0
%convert to latex: http://ericwood.org/excel2latex/
\begin{table}[h]
\center
\caption{Allocation of students for each proposed milestone. Rehman and Amar are masters students who have been partially funded by an NSERC Engage and MITACS. We will hire a two new PhD students and two new masters students.}
\label{tableHQP}
\vspace{+3mm}

\begin{tabular}{  l | c | p{21mm} | p{20mm}  }
\hline
	\textbf{Year} & 1 & 2 & 3 \\ \hline
	1. Test Effectiveness, Test Prioritization, and Test Groups & PhD & PhD & PhD \\ 
	2. Anomalies: Environment vs Product & Rehman &  & \  \\ 
	3. Fault Localization through Test Logs & Amar & Amar (.5) Masters (.5) & Masters \\ 
	4. TestGuru: Risk and History & PhD & PhD \newline Masters &  PhD \newline Masters  \  \\ \hline
	Total students & 4 & 4 & 4 \\ \hline

\end{tabular}

\end{table}

%\vspace{-.5mm}

We plan to recruit a PhD student to work on Milestone 1, which involves test simulations of test prioritization and determining dependent tests. Although there is a wide range of work in this area, the student's research will be conducted in a applied setting and be driven by practical concerns such as which tests cannot be reordered.

Through our NSERC Engage and MITACS our masters student Rehman has conducted work on Milestone 2. He has determined the failure distributions for Ericsson test cases and the report he creates is used by Ericsson developers. He is returning to Concordia to generalize his results. Herzig at Microsoft will be providing anonymized test failure distributions, so that he can determine the degree of anomaly or flakiness of tests at Microsoft. He will also be replicating his work on open source projects including Chrome, which is developed in Montreal. He will be working to integrate his work into TestGuru. He will finish his Masters thesis at the end of the first year of the proposed grant.

Supported by a MITACS, our masters student Amar began work on Milestone 3: fault localization through test logs in February. He has extracted the necessary logs and has begun to iterate over the steps outlined in Section~\ref{secLogs}. He will be supported by the proposed grant for just under two years. We plan to hire an additional masters student to continue work on fault localization.

We plan to recruit a PhD and later a masters student to work on Milestone 4. We will hire two students students to augment data collected in other milestones with historical source code and process data. The PhD student will do novel work in risk analysis and determine where additional tests should be created or modified. The masters student will work with the PhD student to the augmented data to perform test prioritization based on risk. Both students will be responsible for working with Ericsson testers to conduct usability studies of their tools and to integrate them into the Ericsson development process.

